---
title: "Syllabus"
format: 
  html:
    css: styles.css
echo: false
---

**{{< var course.code >}}**: {{< var course.term >}}  with {{< var instructor.name >}} 

---


This course focuses on the physical principles of weather and climate. We cover thermal, moisture and wind dynamics from the scale of ecosystems up to the globe. We also explore daily weather systems and climate change. We discuss large scale weather and climate processes relevant to applications in forestry and agriculture.  This term we will cover:

# Learning Outcomes

* Understand the physical and biological processes that determine the microclimate of a surface.
* Explain how microclimates vary in time & space (vertically and horizontally).
* Describe interactions between the biosphere and the atmosphere, and to understand how surface-atmosphere feedbacks respond to environmental change.
* Know the basic principles of widely used biometeorological instrumentation.
* Analyze and interpret data from measurement systems that are used to monitor near-surface climate and surface radiation and energy balances.
* Provide examples how the principles of biometeorology have practical application to society.



# Important Information


 |
-----|:-----
Lecture|{{< var keyInfo.lecture_time >}} <br> {{< var keyInfo.lecture_room >}}
Remote Attendance|[Via zoom]({{< var keyInfo.zoom >}})
Lecture Recordings|View [here]({{< var keyInfo.recordings >}}) 
TopHat Join Code|{{< var keyInfo.tophat_code >}} 
Piazza Page|Find it [here]({{< var keyInfo.piazza_link >}})



# Course Overview

The course consists of twenty-six 90-minute lectures (with a participation component via TopHat), five lecture review quizzes, seven laboratory exercises, and a final exam.  Important deadlines are listed in @tbl-schedule below.

Lectures will be held in-person. If you are unable to attend in person, lectures will be also be streamed/recorded via zoom you can participate remotely or watch them later.

* **Note**: streaming/recording are a courtesy.  I make no guarantees about the quality of streamed/recorded lectures.  For the best experience, you are encouraged to attend in person.

Labs will also be held in-person. If you are unable to attend a lab, please advise your TA as soon as possible. Once you are enrolled in a lab section (see table below), you must stick to that section throughout the semester.



```{r include=FALSE}

library(knitr)
```


```{r}
#| label: tbl-schedule
#| tbl-cap: "Important Dates"
#| tbl-colwidths: [20,65,15]

DueDates <- read.csv(file = 'sheets/DueDates.csv',sep='|')
kable(DueDates, col.names = gsub("[.]", " ", names(DueDates)))

```

## Evaluation

Lab exercises and the final exam will make up the largest portions of your grade, followed the lecture review quizzes and lecture participation will make up the remaining portion of your grade.  There will also be a few extra credit opportunities over the course of the term.

```{r}
#| label: tbl-grades
#| tbl-cap: "Components of your final grade"
#| tbl-colwidths: [20,30]

grades <- read.csv(file = 'sheets/GradeBreakdown.csv',sep='|')
kable(grades, col.names = gsub("[.]", " ", names(grades)))

```


## Lecture

### Quizzes

### Participation

I encourage you to attend lectures and labs as best as you are able (either in-person on synchronously online). Even if you cannot attend lectures in-person, I expect all student to actively participate in the class. Active participation means that you come to class prepared having read all the materials assigned for each lecture and/or stay up to date on watching lectures and readings even if you are unable to attend lectures. When attending lectures (either in-person on synchronously online), I encourage you to actively participate in discussions and class activities to create an engaging and dynamic learning environment. 

Lectures are held in person {{< var keyInfo.lecture_time >}} in room {{< var keyInfo.lecture_room >}} with a remote attendance option available on [on zoom]({{< var keyInfo.zoom >}}). Recordings will be made available [here]({{< var keyInfo.recordings >}}) for convenience, but lecture participation points are only available **during** keyInfo.

Lecture participation will be gauged using [TopHat](https://tophat.com/students/).  The course **Join Code** is: **{{< var keyInfo.tophat_code >}}**.  

* TopHat questions can **only** be answered during the lecture session
  * They will be available to in person and remote attendees
  * They can be answered via mobile device or laptop
* Questions will be marked based on participation (50%) and correctness (50%)
  * Anonymized answers will be reviewed in lecture to help gauge comprehension

Extra credit will offered at multiple points through the term.

* The course also has a [piazza]({{< var keyInfo.piazza_link >}}) page which can be used to ask/answer questions about assignments and course materials.  Students who are active and helpful on the piazza page will be offered extra participation credit at the end of term.

 


### Lab Assignments

Laboratory exercises are designed to complement the lecture materials and are a mandatory part of the course. The accompanying laboratory exercises provide hands-on experiences explaining physical principles and introducing biometeorological instrumentation.

Late labs: there will be a deduction of 10%/day for late assignments

Collaboration on labs is encouraged. However, you should think about the problems yourself before discussing them with others. Also, write-ups must be done independently. (In practice, this means that it is OK for other people to explain their solutions to you, but you must not be looking at other people's solutions as you write your own.)

Quizzes are available to you from 7am to 11:59pm on the day they are listed in the course schedule above and on Canvas. You will have 20 minutes to complete the quiz once you start it on Canvas. Quizzes are open book, but please make sure to follow the guidelines below on Academic Honesty.

The final exam will be an in-person final scheduled during the scheduled exam period. The final exam will be closed-book.


### Final Exam

The final exam will be will be cumulative, drawing from both lecture and lab material.  It will consist of a flowchart question illustrating how to complete a GIS task, essays/short answers, and miscellaneous fill in the blanks, matching, multiple choice, etc. type questions.  It will be {{< var exam.type >}} and is scheduled for **`r tail(DueDates$Due.Date, 1)`**.  More info will be available closer to the exam date.

# Your Instructor

:::: {.columns}

:::{.column width="30%"}

![](images/{{< var instructor.photo >}}){width=85%}

:::

::: {.column width="70%"}


 |
-----|:-----
Name|{{< var instructor.name >}}
Pronouns|{{< var instructor.pronouns >}}
Email|{{< var instructor.email >}}
Office Hours|{{< var instructor.office >}}


::: 

::::

{{< var instructor.about >}}



# Course Policies

My aim for this semester is to provide a flexible and supportive learning environment while respecting the boundaries of myself and your TAs.  These course policies are intended to establish a framework for navigating the course.

## Feedback & Deadlines 

Lab assignments will be marked by your TA using a standard rubric.  Short comments will be provided where applicable on written answers & map submissions.  Submissions will be accepted without late penalty for {{< var Lab.grace_period >}} days after their due date.

* Quizzes submitted **by the due date** will be graded and returned with feedback {{< var Lab.grace_period >}} days of the due date.
* Late submissions **waive their right** to prompt grading/feedback.  
  * Late quiz submissions **will not** receive feedback from your TA.
  * Late quiz submissions will be marked whenever is convenient for your TA, which could be as late as the end of term
  * After the {{< var Lab.grace_period >}} day grace period, the quiz submission window will **close**, no exceptions.
* This policy only applies to the lab quizzes, **not** the final project or exam.


## Absences

If you are sick (with COVID or otherwise), please stay home to protect others and take care of yourself.  Lectures are streamed [on zoom]({{< var keyInfo.zoom >}}) so that you may still attend online and get TopHat participation credit.  Lecture recordings are also [here]({{< var keyInfo.recordings >}}).  If you miss a lab session, you can attend an alternate session, just make sure to check in with TA running that session.

##  Accommodations

Please contact the [Center for Accessibility](https://students.ubc.ca/about-student-services/centre-for-accessibility) if you require accommodations for a disability.  Once you are registered please make me aware of any necessary accommodations by email in a timely manner.

I will make accommodations on a case by case basis for extenuating circumstances that prevent you completing course work.  It is your responsibility to communicate your needs in a timely fashion (i.e. **before** a due date).

* If you require an accommodation please contact {{< var instructor.name >}} by email: {{< var instructor.email >}}
* My typical approach is to give an alternative assignment rather than giving extensions on lab quizzes because we post the answers after submission deadlines:
  * An alternative lab might consist of writing up an essay or two pertaining to the lecture material + making any maps/figures from the lab, then submitting directly to me by email anytime before the last day of class.

## Academic Concessions

If you require an [Academic Concession](https://www.arts.ubc.ca/degree-planning/academic-performance/academic-concession/) please email me promptly so that we can work together to figure out an accommodation for your situation.  You are not obligated to explain your personal circumstances to me to justify the concession, my intent is to be accommodating.  However, you must to communicate any need for a concession in a timely manner.  If you require multiple concessions I may refer you to [Arts Advising](https://www.arts.ubc.ca/student-support/academic-support/academic-advising/).


## Academic Integrity

The academic enterprise is founded on honesty, civility, and integrity. As members of this enterprise, all students are expected to know, understand, and follow the codes of conduct regarding academic integrity. At the most basic level, this means submitting only original work done by you and acknowledging all sources of information or ideas and attributing them to others as required. This also means you should not cheat, copy, or mislead others about what is your work. Violations of academic integrity (i.e., misconduct) lead to the breakdown of the academic enterprise, and therefore serious consequences arise and harsh sanctions are imposed.

Plagiarism and cheating will be taken very seriously.  The first incident of plagiarism/copying/cheating will result in a zero for the assignment.  Further incidents will be reported to the President’s Advisory Committee on Student Discipline in addition to a zero.  A more detailed description of academic integrity, including the University’s policies and procedures, may be found [here](https://learningcommons.ubc.ca/academic-integrity/Links)

Though you may work together with your classmates on the assignments and help each other, ALL STUDENTS MUST SUBMIT THEIR OWN ORIGINAL WORK. This means that your maps must be your own, and your answers must be in your own words. Failure to submit your own work can result in failing the assignment or worse, so please be careful. See the Academic Integrity section of the Syllabus for more information.

# Strategies for Success

**Be proactive!** 

* Keep track of deadlines & note the late submission policies
  * Timely communication is important!  If you have an issue, please bring it to my attention.
  * Partial credit is better than no credit.  If you can't finish a lab before the deadline - just submit what you've got done already. 
* Drop by office hours & ask questions!
* Don't wait until the last minute to set up ArcGIS Pro, do it now to save yourself a headache down the road.