---
title: "General Info"
format: 
  html:
    css: styles.css
echo: false
---

```{r include=FALSE}

library(knitr)
```

Labs will be held weekly (excluding the first week of term) in room 102A of the Macmillan building.  Times for each lab section and information for the corresponding TAs are listed at the bottom of this page.  You **must** be registered for a lab section in order to complete the course.


# Expectations and Rules

## Lab materials 

All equipment necessary to conduct laboratory experiments will be provided; however, it is the responsibility of the student to bring to each class the laboratory instructions (a paper copy or online version), an adequate. Copies of the lecture notes / slides may be useful.

## Formatting

Laboratory reports should be written concisely and uploaded as a Word Document of PDF to Canvas. Number and sort your answers in accordance with questions in lab manual. All questions should be attempted and answered in the order of the lab manual. Answers should be presented in tables where possible. For selected exercises, empty templates are provided on the course web-page. No need to repeat questions. Procedures and equipment should also not be reported. Any calculations with important results should be clearly indicated. In some cases an analysis of errors is appropriate. Please always indicate units and follow the SI for units and scientific notation (see Lecture 1). The report's header should list the course number, your name, your UBC student number, your TA's name, and the number and title of the lab.

## Due date

All reports should be submitted on Canvas by the due date. Late lab reports will be penalized 10% per day. Lab reports will not be accepted once graded reports have been returned to the class. In cases where a student fails to submit a report due to sickness, they should contact the current TA before the deadline to discuss options.

## Grading of reports

TAs are responsible for grading all lab report, which vary between 8.5 to 15 points each depending on the lab. All eight labs together contribute 40% to the course's final grade. The break-down of the marking in each lab is indicated in square brackets following each question. It will often be necessary to consult the reading material, lecture slides and notes, or other sources in order to provide good answers to these questions. Top marks will generally be assigned only where perceptive and appropriate interpretative comments are presented in addition to all observations and answers specifically requested.

# Lab Times

```{r}

Labs <- read.csv(file = 'sheets/LabTimes.csv',sep='|')
kable(Labs)

```

## Your TAs

:::: {.columns}

:::{.column width="30%"}

![](images/{{< var Lab.TA1.photo >}}){width=85%}

:::

:::{.column width="70%"}

 |
-----|:-----
Name|{{< var Lab.TA1.name >}}
Pronouns|{{< var Lab.TA1.pronouns >}}
Email|{{< var Lab.TA1.email >}}
Office|{{< var Lab.TA1.office >}}


::: 

::::

{{< var Lab.TA1.about >}}

---

:::: {.columns}

:::{.column width="30%"}

![](images/{{< var Lab.TA2.photo >}}){width=85%}

:::

:::{.column width="70%"}


 |
-----|:-----
Name|{{< var Lab.TA2.name >}}
Pronouns|{{< var Lab.TA2.pronouns >}}
Email|{{< var Lab.TA2.email >}}
Office|{{< var Lab.TA2.office >}}

::: 

::::

{{< var Lab.TA2.about >}}

---

:::: {.columns}

:::{.column width="30%"}

![](images/{{< var Lab.TA3.photo >}}){width=85%}

:::

:::{.column width="70%"}


 |
-----|:-----
Name|{{< var Lab.TA3.name >}}
Pronouns|{{< var Lab.TA3.pronouns >}}
Email|{{< var Lab.TA3.email >}}
Office|{{< var Lab.TA3.office >}}

::: 

::::

{{< var Lab.TA3.about >}}




# Your TAs 

